\inputencoding{utf8}
\HeaderA{explicit.model}{Explicit Equations}{explicit.model}
\keyword{method}{explicit.model}
%
\begin{Description}\relax
\code{explicit.model} is the system evaluation function called when neither
\$ODE or \$DDE blocks are detected in the model file, indicating that the model
is defined by explicit equations. \code{explicit.model} is typically not 
called directly by users.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
  explicit.model(parms = NULL,
                 derparms = NULL,
                 code = NULL,
                 bolus = NULL,
                 infusion = NULL,
                 xdata = NULL,
                 covdata = NULL,
                 issim = 0,
                 check = FALSE)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{parms}] A vector of primary parameters.
\item[\code{derparms}] A list of derived parameters, specified in the \$DERIVED block
of code. (NULL for \code{explicit.model}).
\item[\code{code}] A list of R code extracted from the model file. Depending on 
content of the model file, the levels of this list could be: template,
derived, lags, ode, dde, output, variance, and/or secondary.
\item[\code{bolus}] A data.frame providing the instantaneous inputs  entering the 
system of delay differential equations for the treatment and individual 
being evaluated.
\item[\code{infusion}] A data.frame providing the zero-order inputs entering the 
system of delay differential equations for the treatment and individual 
being evaluated.
\item[\code{xdata}] A vector of times at which the system is being evaluated.
\item[\code{covdata}] A data.frame of covariate data for the treatment and individual 
being evaluated.
\item[\code{issim}] An indicator for simulation or estimation runs.
\item[\code{check}] An indicator whether checks should be performed to validate 
function inputs.
\end{ldescription}
\end{Arguments}
%
\begin{Details}\relax
\code{explicit.model} evaluates the model for each treatment of each 
individual contained in the dataset, based upon the code specified in the 
\$OUTPUT block in the model file.
\end{Details}
%
\begin{Value}
Returns a matrix of system predictions.
\end{Value}
%
\begin{Author}\relax
Sebastien Bihorel (\email{sb.pmlab@gmail.com})
\end{Author}
