\inputencoding{utf8}
\HeaderA{initialize.report}{Initialize Report Files}{initialize.report}
\keyword{method}{initialize.report}
%
\begin{Description}\relax
\code{initialize.report} is a secondary function called during direct grid 
search or estimation runs. 

For direct grid search runs, \code{initialize.report} creates the report file 
in the results \& backup directory. This report file reports information about 
the run, including a summary table of the grid search which gives the value of 
the objective function for the different vector of estimates tested.

For estimation runs, \code{initialize.report} creates the log file and the 
report file in the results \& backup directory. The log file stores, for each 
subject in the analysis, the values of the objective function and the 
parameter estimates at each iteration of the estimation process. The report 
file reports information about the estimation run, including the final 
estimates and some related statistics.

\code{initialize.report} is typically not called directly by users.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
  initialize.report(problem = NULL,
                   param = NULL,
                   files = NULL,
                   isgrid = 0)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{problem}] A list containing the following levels:\begin{description}

\item[data] A list which content depends on the scope of the analysis. If 
the analysis was run at the level of the subject, \code{data} contains as 
many levels as the number of subjects in the dataset, plus the \code{ids}
level containing the vector of identification numbers of all subjects 
included in the analysis population. If the analysis was run at the level 
of the population, \code{data} contains only one level of data and 
\code{ids} is set to 1.

Each subject-specific level contains as many levels as there are treatment
levels for this subject, plus the \code{trts} level listing all treatments
for this subject, and the \code{id} level giving the identification number
of the subject. 

Each treatment-specific levels is a list containing the following levels: 
\begin{description}

\item[cov] mij x 3 data.frame containing the times of observations of the
dependent variables (extracted from the TIME variable), the indicators
of the type of dependent variables (extracted from the CMT variable),
and the actual dependent variable observations (extracted from the 
DV variable) for this particular treatment and this particular 
subject.
\item[cov] mij x c data.frame containing the times of observations of 
the dependent variables (extracted from the TIME variable) and all the
covariates identified for this particular treatment and this 
particular subject.
\item[bolus] bij x 4 data.frame providing the instantaneous inputs 
for a treatment and individual.
\item[infusion] fij x (4+c) data.frame providing the zero-order inputs for
a treatment and individual.
\item[trt] the particular treatment identifier.
\end{description}


\item[method] A character string, indicating the scale of the analysis. Should
be 'population' or 'subject'.
\item[init] A data.frame of parameter data with the following columns:
'names', 'type', 'value', 'isfix', 'lb', and 'ub'.
\item[debugmode] Logical indicator of debugging mode.
\item[modfun] Model function.

\end{description}


\item[\code{param}] A data.frame containing the values of fixed and variable 
parameter estimates. Expected to contain the 'names', 'type', 'value',
'isfix', 'lb', and 'ub' columns.
\item[\code{files}] A list of input used for the analysis. The following elements are
expected and none of them could be null: \begin{description}

\item[data] A .csv file located in the working directory, which contains
the dosing information, the observations of the dependent variable(s)
to be modeled, and possibly covariate information. The expected format 
of this file is described in details in \code{vignette('scaRabee',
        package='scaRabee')}.
\item[param] A .csv file located in the working directory, which contains
the initial guess(es) for the model parameter(s) to be optimized or used
for model simulation. The expected format of this file is described in
details in \code{vignette('scaRabee',package='scaRabee')}.
\item[model] A text file located in the working directory, which defines 
the model. Models specified with explicit, ordinary or delay 
differential equations are expected to respect a certain syntax and 
organization detailed in \code{vignette('scaRabee',package='scaRabee')}.
\item[iter] A .csv file reporting the values of the objective function
and estimates of model parameters at each iteration.
\item[report] A text file reporting for each individual in the dataset the
final parameter estimates for structural model parameters, residual 
variability and secondary parameters as well as the related statistics 
(coefficients of variation, confidence intervals, covariance and 
correlation matrix).
\item[pred] A .csv file reporting the predictions and calculated residuals
for each individual in the dataset.
\item[est] A .csv file reporting the final parameter estimates for each
individual in the dataset.
\item[sim] A .csv file reporting the simulated model predictions for each 
individual in the dataset. (Not used for estimation runs).

\end{description}


\item[\code{isgrid}] Indicator of direct grid search runs.
\end{ldescription}
\end{Arguments}
%
\begin{Author}\relax
Sebastien Bihorel (\email{sb.pmlab@gmail.com})
\end{Author}
