\inputencoding{utf8}
\HeaderA{scarabee.new}{Create a scaRabee Analysis Folder}{scarabee.new}
\keyword{method}{scarabee.new}
%
\begin{Description}\relax
\code{scarabee.new} creates a new \pkg{scaRabee} analysis folder.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
  scarabee.new(name = 'myanalysis',
               path = NULL,
               type = 'simulation',
               method = 'population',
               template = 'ode')
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{name}] A string of characters defining the name of the master analysis
script; \code{name} is also appended to the \$ANALYSIS tag in the model file.
Default is 'myanalysis'.
\item[\code{path}] A path where the analysis files must be created. The path must 
not yet exist.
\item[\code{type}] A string of characters, either 'simulation', 'estimation', or 
'gridsearch'. Default is 'simulation'.
\item[\code{method}] A string of characters, either 'population' or 'subject'.
Default is 'population'.
\item[\code{template}] A string of characters, either 'explicit', 'ode' or 'dde'.
Default is 'ode'.
\end{ldescription}
\end{Arguments}
%
\begin{Details}\relax
The content of new \pkg{scaRabee} analysis folder \code{path}/
is:\begin{description}

\item[\code{name}.R] The template-based \pkg{scaRabee} analysis script.
\item[model.txt] A template-based txt file for the definition of the
structural model. Depending on \code{template}, this text file contains
various tags which delimit blocks of R code needed when models are defined
with closed form solution ('explicit'), ordinary differential equations 
('ode') or delay differential equations ('dde').
\item[data.csv] (optional) An empty comma-separated file for dosing, 
observations, and covariate information; contains the following default
headers: OMIT, TRT, ID, TIME, AMT, RATE, CMT, EVID, DV, DVID, and MDV.
\item[initials.csv] (optional) An empty comma-separated file for initial
guesses of model parameter estimates; contains the following default
headers: Parameter, Type, Value, Fixed, Lower bound, Upper bound.

\end{description}


If the \code{path} argument is NULL, then it is coerced to \code{name}, thus 
creating a new folder in the current working directory.

See \code{vignette('scaRabee',package='scaRabee')} to learn about how to
specify your model based on those template files.
\end{Details}
%
\begin{Author}\relax
Sebastien Bihorel (\email{sb.pmlab@gmail.com})
\end{Author}
