\inputencoding{utf8}
\HeaderA{scarabee.analysis}{Run a scaRabee analysis}{scarabee.analysis}
\keyword{method}{scarabee.analysis}
%
\begin{Description}\relax
\code{scarabee.analysis} is the \emph{de facto} gateway for running any kind 
of analysis with \pkg{scaRabee}. All other functions distributed with this
package are secondary functions called directly or indirectly by
\code{scarabee.analysis}.

Arguments for \code{scarabee.analysis} are best defined using the template
distributed with the package.

\end{Description}
%
\begin{Usage}
\begin{verbatim}
  scarabee.analysis(files = NULL,
                    states = NULL,
                    runtype = NULL,
                    debugmode = FALSE,
                    estim.options = NULL,
                    analysis = 'myanalysis')
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{files}] A list of input used for the analysis. The following elements are
expected and none of them could be null: \begin{description}

\item[data] A .csv file located in the working directory, which contains
the observations of the dependent variable(s) to be modeled. The
expected format of this file is described in details in
\code{vignette('scaRabee',package='scaRabee')}.
\item[param] A .csv file located in the working directory, which contains
the initial guess(es) for the model parameter(s) to be optimized or used
for model simulation. The expected format of this file is described in
details in \code{vignette('scaRabee',package='scaRabee')}.
\item[dose] A .csv file located in the working directory, which contains
the dosing information. The expected format of this file is described in
details in \code{vignette('scaRabee',package='scaRabee')}.
\item[cov] A .csv file located in the working directory, which contains
the values of one or more covariates that may or may or be used within
the model. The expected format of this file is described in details in
\code{vignette('scaRabee',package='scaRabee')}.
\item[model] A .R file located in the 'model.definition'
sub-directory in the working directory, which defines the model. Models
specified with explicit, ordinary or delayed differential equations
should be preferentially defined using the provided templates. More
details about the expected structure of this file is provided in
\code{vignette('scaRabee',package='scaRabee')}, in case the user would
want to develop her/his own template.
\item[var] A .R file located in the 'model.definition' sub-directory
in the working directory, which defines the model of residual
variability. More details about the expected content of this file is
provided in \code{vignette('scaRabee',package='scaRabee')}.
\item[sec] A .R file located in the 'model.definition' sub-directory
in the working directory, which defines the method of computation of
secondary parameters (derived from the fixed or estimated model
parameters). More details about the expected content of this file is
provided in \code{vignette('scaRabee',package='scaRabee')}.

\end{description}


\item[\code{states}] A vector of integers, indicating which model states should be
associated with model predictions. Only used in simulation runs.
\item[\code{runtype}] A character string, indicating the type of analysis. Should be
'simulation' or 'estimation'.
\item[\code{debugmode}] A logical value, indicating the debug mode should be turn on
(\code{TRUE}) or off (default). Used only for estimation runs. If turn on,
the user could have access to error message returned when the model and
residual variability are evaluated in \code{fitmle} before the likelihood
is computed.
\item[\code{estim.options}] A list of estimation options containing two elements
\code{maxiter} (the maximum number of iterations) and \code{maxeval} (the
maximum number of function evaluations).
\item[\code{analysis}] A character string, defining the 'title' of the run that will
be used to name the output files of the analysis. If
\code{scarabee.analysis} is called within \code{script.R}, a file created
from the provided template , \code{analysis} will be 'script'.
\end{ldescription}
\end{Arguments}
%
\begin{Value}
Run an analysis until completion. See 
\code{vignette('scaRabee',package='scaRabee')} for more details about the
expected outputs for an estimation or a simulation run.
\end{Value}
%
\begin{Author}\relax
Sebastien Bihorel (\email{sb.pmlab@gmail.com})
\end{Author}
%
\begin{SeeAlso}\relax
\code{\LinkA{fitmle}{fitmle}}
\end{SeeAlso}
