\inputencoding{utf8}
\HeaderA{scarabee.new}{Create a scaRabee Analysis Folder}{scarabee.new}
\keyword{method}{scarabee.new}
%
\begin{Description}\relax
\code{scarabee.new} creates a new \pkg{scaRabee} analysis folder.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
  scarabee.new(name = 'myanalysis',
               path = getwd(),
               type = 'simulation',
               template = 'ode',
               with.inputs = TRUE)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{name}] A string of characters defining the name of the new folder; 
\code{name} is also used to name the \pkg{scaRabee} analysis script. Default
is 'myanalysis'.
\item[\code{path}] A path where the new folder is created. Default is the current
working directory.
\item[\code{type}] A string of characters, either 'simulation' or 'estimation'.
Default is 'simulation'.
\item[\code{template}] A string of characters, either 'explicit', 'ode' or 'dde'.
Default is 'ode'.
\item[\code{with.inputs}] A logical indicator whether template input files should be
created or not. Default is TRUE.
\end{ldescription}
\end{Arguments}
%
\begin{Details}\relax
The content of new \pkg{scaRabee} analysis folder (\code{path}/\code{name})
is:\begin{description}

\item[model.definition] A sub-folder containing: \begin{description}

\item[model.R] A template-based R script for the definition of the
structural model. Depending on \code{template}, it is either based on
a template for model defined with closed form solution ('explicit'),
ordinary differential equations ('ode') or delay differential
equations ('dde').
\item[weighting.R] A template-based R script for the definition of the
residual variability model.
\item[secondary.R] A template-based R script for the definition of
secondary parameters.

\end{description}


\item[\code{name}.R] The template-based \pkg{scaRabee} analysis script.
\item[data.csv] (optional) An empty comma-separated file for system
observations; contains the following default headers: Dose ID, Time,
Y(1).
\item[dosing.csv] (optional) An empty comma-separated file for dosing
events; contains the following default headers: Dose ID, Time, State,
Bolus, Infusion Rate.
\item[initials.csv] (optional) An empty comma-separated file for initial
guesses of model parameter estimates; contains the following default
headers: Parameter, Type, Value, Fixed, Lower bound, Upper bound.
\item[covariates.csv] (optional) An empty comma-separated file for covariate
observations; contains the following default headers: Dose ID, Time,
Cov(1).

\end{description}

See \code{vignette('scaRabee',package='scaRabee')} to learn about how to
specify your model based on those template files.
\end{Details}
%
\begin{Author}\relax
Sebastien Bihorel (\email{sb.pmlab@gmail.com})
\end{Author}
