\inputencoding{utf8}
\HeaderA{scarabee.read.parms}{Read scaRabee Parameter File}{scarabee.read.parms}
\keyword{method}{scarabee.read.parms}
%
\begin{Description}\relax
\code{scarabee.read.parms} is a secondary function called at each 
\pkg{scaRabee} run. It reads and checks the information contained in the 
specified parameter file.\code{scarabee.read.parms} is typically not called
directly by users.
\end{Description}
%
\begin{Usage}
\begin{verbatim}
  scarabee.read.parms(files = NULL)
\end{verbatim}
\end{Usage}
%
\begin{Arguments}
\begin{ldescription}
\item[\code{files}] A list of input used for the analysis. The following elements are
expected and none of them could be null: \begin{description}

\item[data] A .csv file located in the working directory, which contains
the dosing information, the observations of the dependent variable(s)
to be modeled, and possibly covariate information. The expected format 
of this file is described in details in \code{vignette('scaRabee',
        package='scaRabee')}.
\item[param] A .csv file located in the working directory, which contains
the initial guess(es) for the model parameter(s) to be optimized or used
for model simulation. The expected format of this file is described in
details in \code{vignette('scaRabee',package='scaRabee')}.
\item[model] A text file located in the working directory, which defines 
the model. Models specified with explicit, ordinary or delay 
differential equations are expected to respect a certain syntax and 
organization detailed in \code{vignette('scaRabee',package='scaRabee')}.
\item[iter] A .csv file reporting the values of the objective function
and estimates of model parameters at each iteration.  (Not used for 
simulation runs).
\item[report] A text file reporting for each individual in the dataset the
final parameter estimates for structural model parameters, residual 
variability and secondary parameters as well as the related statistics 
(coefficients of variation, confidence intervals, covariance and 
correlation matrix). (Not used for simulation runs).
\item[pred] A .csv file reporting the predictions and calculated residuals
for each individual in the dataset. (Not used for simulation runs).
\item[est] A .csv file reporting the final parameter estimates for each
individual in the dataset. (Not used for simulation runs).
\item[sim] A .csv file reporting the simulated model predictions for each 
individual in the dataset. (Not used for estimation runs).

\end{description}


\end{ldescription}
\end{Arguments}
%
\begin{Value}
If the content of the parameter file is valid, \code{scarabee.read.parms}
returns a data.frame with the same content. The names of the data.frame 
columns are: names, type, value, isfix, lb, and ub.
\end{Value}
%
\begin{Author}\relax
Sebastien Bihorel (\email{sb.pmlab@gmail.com})
\end{Author}
%
\begin{SeeAlso}\relax
\code{\LinkA{scarabee.analysis}{scarabee.analysis}}
\end{SeeAlso}
